Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-09-14 paper.qmd
Add contributions

>>>>

## Author contributions {.unnumbered}

<!-- Conceptualization
Data curation
Formal analysis
Funding acquisition
Investigation
Methodology
Project administration
Software
Resources
Supervision
Validation
Visualization
Writing – original draft
Writing – review & editing -->

RL, JT, EVT, HM: Conceptualization, Methodology, Formal analysis, Validation, Writing – original draft, Writing – review & editing

EB, PW, GOT: Project administration, Validation

DB, SM: Resources, Validation, Project administration, Funding acquisition
